---
title: "01. Exploratory Data Analysis"
author: "Jin-Hoon An"
date: '2017 11 29 '
output: html_document
mainfont: AppleGothic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- RMD 설정 -->
```{r, include=F}
Sys.setenv("LANGUAGE"="EN")

library(ggplot2)
theme_set(theme_gray(base_family='NanumGothic')) # 한글깨짐 방지

library(dplyr)
library(ggplot2)
library(ISLR)
library(MASS)
library(glmnet)
library(randomForest)
library(gbm)
library(rpart)
library(boot)
library(rpart)
library(hacktoolkit)
library(ROCR)
```

### Contingency table review

> Excercise

In this chapter you'll continue working with the comics dataset introduced in the video. This is a collection of characteristics on all of the superheroes created by Marvel and DC `comics` in the last 80 years.

Let's start by creating a contingency table, which is a useful way to represent the total counts of observations that fall into each combination of the levels of categorical variables.

> Instructions

The dataset has been loaded into your workspace as `comics`.

- Type the name of the dataset to look at the rows and columns of the dataset.
- View the `levels()` that the `align` variable can take.
- View the `levels()` that the `gender` variable can take.
- Create a contingency table of the same two variables.


```{r}
# Print the first rows of the data
#comics

# Check levels of align
#levels(comics$align)

# Check the levels of gender
#levels(comics$gender)

# Create a 2-way contingency table
#table(comics$align, comics$gender)
```
